---
title: Analysis of 10 x 6 hour experiments with 5 params, 10 input steps, fixed duration, 5 mins for OID
author: "Ally Hume"
date: "25 January 2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Description

* Experiment name: Leia
* Each run executed 10 OID-Experiment-PE loops. 
* Using gal1 no-delay model
* Only the fluoresence state was observable.
* Parameters alpha2, d2, Kf and Kb were fixed to the true value of 1.
* The system tried to fit alpha1, Vm1, h1, Km1 and d1.
* The range for parameters alpha1, Vm1, Km1 and d1 was 0.1 times the true value to 10 times the true value.
* The range for parameter h1 was 0 to 4 (true was 2.225)
* Each experiement was independent from the other experiments and lasted for 6 hours.
* Experiments were sampled every 5 mins.
* OID used eSS with fmincon and a 5 minute maximum duration
* OID used Emod-optimality
* The input stimulus was stepped with 10 steps (values between 0 and 2)
* The input stimulus steps were of fixed duration.
* Mocked experiments always start from the equilibrum state
* Hetero noise was added to output with a standard deviation of 10% of the value.
* PE used eSS with lsqnonlin and a 5 minute maximum duration.
* PE used the log likelhood cost function.

```{r echo=FALSE, warning=FALSE, error=FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
library(reshape2)
library(knitr)

trueValues = data.frame( param=c("alpha1","Vm1","h1","Km1","d1","alpha2","d2","Kf","Kb"),
                         trueValue=c(0.00175985449291231,0.0800887345690361,2.22548971250921,3.35948035905386,0.0100614569676223,1,1,1,1) )

load_experiment_data <- function(filename) {
  
  wholeFile <- readLines(filename)
  iterationData <- wholeFile[grep('ITERATION',wholeFile)]
  iterationData <- iterationData[grep('PARAM_FIT|REL_CONF',iterationData)]
  con <- textConnection(iterationData)
  data <- read.table(con)
  close(con)
  
  colnames(data) <- c("key", "iteration", "type", "param", "value")
  
  data <- data %>% mutate( runName = gsub('.dat','',filename))
  
  return(data)
}

# Get the data files.
files <- list.files(pattern='Leia.*dat')

# Read in each file, convert to a data frame and merge into one dataframe
data <- lapply(files, load_experiment_data)
data <- Reduce(function(...) merge(..., all=T), data)

# Join data with true values
data <- left_join(data,trueValues)
```

## Number of runs

```{r echo=FALSE}
d <- data %>% filter(type == 'PARAM_FIT' & iteration == 10 & param == 'alpha1')
d <- d %>% summarise(n=n())
kable(d)
```

## Fitted parameter values after final iteration

```{r echo=FALSE}
d <- data %>% filter(type == 'PARAM_FIT' & iteration == 10) %>% 
     select(param, trueValue, value) %>% 
     group_by(param, trueValue) %>% 
     summarize( mean=mean(value), sd=sd(value), min=min(value), max=max(value))
kable(d)
```

Plotted as a box plot diagram:

```{r echo=FALSE}
d <- data %>% filter(type == 'PARAM_FIT' & iteration == 10) %>% 
     select(param, trueValue, value) 

ggplot(data=d, aes(x=factor(1),y=value)) + 
#  geom_jitter(alpha=0.3,  color="tomato") +
  geom_boxplot(alpha=0) + facet_wrap(~ param, scales = "free_y") +
  geom_hline(aes(yintercept=trueValue), color='red') +
  theme(axis.text.x=element_blank(),
        axis.title.x=element_blank(), 
        axis.title.y = element_blank()) 
```

Or as histograms:

```{r echo=FALSE}
d <- data %>% filter(type == 'PARAM_FIT' & iteration == 10) %>% 
     select(param, value) 

ggplot(data=d, aes(value)) + geom_histogram(bins=15) + facet_wrap( ~ param, scales="free")

```

Plotting scatter plots of the fitted parameter values show correlations between:

* alpha1 - d1
* h1 - Km1
* h1 - Vm1
* Km1 - Vm1
     
```{r echo=FALSE}
d <- data %>% filter(type == 'PARAM_FIT' & iteration == 10) %>% 
     select(runName,param,value)
d <- reshape(d, timevar="param", idvar=c("runName"), direction="wide")
d <- d %>% select(alpha1=value.alpha1, d1=value.d1, h1=value.h1, Km1=value.Km1, Vm1=value.Vm1)

pairs(d)
```

## Relative confidence intervals after the final iteration

```{r echo=FALSE}
d <- data %>% filter(type == 'REL_CONF' & iteration == 10) %>% 
     select(param, value) %>% 
     group_by(param) %>% 
     summarize( mean=mean(value), sd=sd(value))
kable(d)
```

```{r echo=FALSE}
d <- data %>% filter(type == 'REL_CONF' & iteration == 10) %>% 
     select(param, value) 

ggplot(data=d, aes(value)) + geom_histogram(bins=15) + facet_wrap( ~ param, scales="free")

```

There is a very strong correlation between the relative confidence intervals of Km1 and Vm1.

```{r echo=FALSE}
d <- data %>% filter(type == 'REL_CONF' & iteration == 10) %>% 
     select(runName,param,value)
d <- reshape(d, timevar="param", idvar=c("runName"), direction="wide")
d <- d %>% select(alpha1=value.alpha1, d1=value.d1, h1=value.h1, Km1=value.Km1, Vm1=value.Vm1)

pairs(d)
```

## Are relative confidence intervals larger for the poorer fits?

```{r echo=FALSE, message=FALSE}
d <- data %>% filter(type == 'REL_CONF' & iteration == 10) %>% 
     select(runName,param,relconf=value)
d2 <- data %>% filter(type == 'PARAM_FIT' & iteration == 10) %>% 
     select(runName,param,value)
d <- d %>% left_join(d2) %>% select(param, value, relconf) 

ggplot(data=d, aes(x=value,y=relconf)) + geom_point(shape=1) + facet_wrap( ~ param, scales="free")
```

For Km1 and Vm1 the highest relative confidence intervals are associated with the higher (and most incorrect) parameter estimates. I had hoped we would maybe see U-shaped plots where parameter estimates much lower than the true value also correspond to high relative confidence intervals. We are not seeing such an effect in these plots.
